Sets

### 2023-10-03 rec06/paper.tex
intersection

Given a set $w$, there is a \emph{subcollection} of $w$ whose elements satisfy certain property $\varphi$.
\[
  \{ x \in w \mid \varphi(x) \}
\]
We declare that such subcollections are sets.

@@

In \cref{eg:subsets}, $\{ a,b,c \}$ has subsets $\varnothing$, $\{ a \}$, $\{ b \}$, $\{ c \}$, $\{ a,b \}$, $\{ a,c \}$, $\{ b,c \}$, and $\{ a,b,c \}$.
These subsets form a collection
\[
  \{ \varnothing, \{ a \}, \{ b \}, \{ c \}, \{ a,b \}, \{ a,c \}, \{ b,c \}, \{ a,b,c \} \}
\]
We declare that such a collection is a set.

@@

@@

>>>>

Given a set $w$, there is a set of $w$ whose elements satisfy certain property $\varphi$.
\[
  \{ x \in w \mid \varphi(x) \}
\]

@@

In \cref{eg:subsets}, $\{ a,b,c \}$ has subsets $\varnothing$, $\{ a \}$, $\{ b \}$, $\{ c \}$, $\{ a,b \}$, $\{ a,c \}$, $\{ b,c \}$, and $\{ a,b,c \}$.
These subsets form a set
\[
  \{ \varnothing, \{ a \}, \{ b \}, \{ c \}, \{ a,b \}, \{ a,c \}, \{ b,c \}, \{ a,b,c \} \}
\]

@@

\begin{defn}
  Given a nonempty set of sets $\cF$, the \emph{union}, denoted $\cup\cF$, is a set whose elements are those elements of \emph{some} set in $\cF$.
\end{defn}

\begin{eg}
  \begin{enumerate}
  \item[]
  \item If $\cF = \{\{1,2,3\},\{a,b,c\}\}$ then $\cup\cF = \{1,2,3,a,b,c\}$.
  \item If $\cF = \{\{a,b,c\},\{b,c,d\},\{c,d,e\}\}$ then $\cup\cF = \{a,b,c,d,e\}$.
  \end{enumerate}
\end{eg}

\begin{notn}
  When $\cF$ has just a few elements, for example $\cF = \{\{1,2,3\},\{a,b,c\}\}$, we write
  \[
    \{1,2,3\} \cup \{a,b,c\}
  \]
  for $\cup\cF$.
\end{notn}

@@

\begin{defn}
  Given a nonempty set of sets $\cF$, the \emph{intersection}, denoted $\cap\cF$, is a set whose elements are those elements of \emph{every} set in $\cF$.
\end{defn}

\begin{eg}
  \begin{enumerate}
  \item[]
  \item If $\cF = \{\{1,2,3\},\{a,b,c\}\}$ then $\cap\cF = \varnothing$.
  \item If $\cF = \{\{a,b,c\},\{b,c,d\},\{c,d,e\}\}$ then $\cap\cF = \{c\}$.
  \end{enumerate}
\end{eg}

\begin{notn}
  When $\cF$ has just a few elements, for example $\cF = \{\{1,2,3\},\{a,b,c\}\}$, we write
  \[
    \{1,2,3\} \cap \{a,b,c\}
  \]
  for $\cap\cF$.
\end{notn}
